The ChEMBL database as Linked Open Data

### 2012-07-19 article.tex
I'm the corresponding author

\author{Egon~L.~Willighagen$^{1}$\email{Egon~L.~Willighagen - egon.willighagen@maastrichtuniversity.nl}\and
Andra~Waagmeester$^1$\email{Andra Waagmeester - FIXME}\and
Ola Spjuth$^2$\email{Ola Spjuth - FIXME}\and
Peter~Ansell$^3$\email{Peter Ansell - p\_ansell@yahoo.com}\and
Antony~Williams$^4$\email{Antony Williams - FIXME}\and
Valery~Tkachenko$^4$\email{Valery Tkachenko - FIXME}\and
Janna~Hastings$^5$\email{Janna Hastings - FIXME}\and
John~Overington$^6$\email{John Overington - FIXME}\and
Anna~Gaulton$^6$\email{Anna Gaulton - FIXME}\and
Mark~Davies$^6$\email{Mark Davies - FIXME}\and
Bin~Chen$^7$\email{Bin Chen - FIXME}\and
David~Wild$^7$\email{David Wild - FIXME}
}

>>>>

\author{Egon~L.~Willighagen$^{1,*}$\email{Egon~L.~Willighagen - egon.willighagen@maastrichtuniversity.nl}\and
Andra~Waagmeester$^1$\email{Andra Waagmeester - FIXME}\and
Ola Spjuth$^2$\email{Ola Spjuth - FIXME}\and
Peter~Ansell$^3$\email{Peter Ansell - p\_ansell@yahoo.com}\and
Antony~Williams$^4$\email{Antony Williams - FIXME}\and
Valery~Tkachenko$^4$\email{Valery Tkachenko - FIXME}\and
Janna~Hastings$^5$\email{Janna Hastings - FIXME}\and
John~Overington$^6$\email{John Overington - FIXME}\and
Anna~Gaulton$^6$\email{Anna Gaulton - FIXME}\and
Mark~Davies$^6$\email{Mark Davies - FIXME}\and
Bin~Chen$^7$\email{Bin Chen - FIXME}\and
David~Wild$^7$\email{David Wild - FIXME}
}
